---
title: "Parliament Elections Analysis 1951 - 2009"
author: "Navneeth I U"
date: "15 September 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
parliament = read.csv("C://Users//Administrator//Documents//EDA//CSV//parliament.csv")
library(knitr)
library(dplyr)
library(zoo)
library(ggplot2)
View(parliament)
```

### Percentage of null values in all column 
```{r}
col.na= colSums(is.na(parliament))*100/nrow(parliament)
col.na
```

### Percentage of data availability 
```{r}
col.na= colSums(!is.na(parliament))*100/nrow(parliament)
col.na
```

### Identify year wise total number of electors and voters? Also compute percentage of voters.
```{r, message=FALSE, warning=FALSE}
Total_electors_voters = parliament %>% group_by(YEAR) %>% summarise(TOTAL_VOTERS=sum(VOTES,na.rm=TRUE), TOTAL_ELECTORS=sum(unique(ELECTORS),na.rm=TRUE),PERCENT_VOTERS=(TOTAL_VOTERS/TOTAL_ELECTORS*100))
kable(Total_electors_voters)
```

####In the above output we can observe that the voters per election does not exceed 70% 


### Identify year wise percentage of male and female candidates?
```{r, message=FALSE, warning=FALSE}
parliament = parliament %>% mutate(Male = if_else(SEX=="M",1,0))
parliament = parliament %>% mutate(Female = if_else(SEX=="F",1,0))
Year_wise_candidates = parliament %>% group_by(YEAR) %>% summarise(PERCENT_MALE = sum(Male)/n()*100, PERCENT_FEMALE = sum(Female)/n()*100)
kable(Year_wise_candidates)
```

#### In the output we observe that male candidates in every election exceeds 90% and in the year 1971 there was zero female candidates


### Compute partywise total number of candidates won so far? Display top ten parties alone
```{r, message=FALSE, warning=FALSE}
Top_parties = parliament %>% filter(Position==1) %>% group_by(PARTY) %>% summarise(CONSTITUENCY_VICTORIES = n()) %>% arrange(-CONSTITUENCY_VICTORIES)
kable(Top_parties[1:10,])
```

#### We can observe that Patry INC has won most number of constituencies by a huge margin


### Identify yearwise which party has won (based on total number of constituencies won)
```{r, message=FALSE, warning=FALSE}
Year_result = parliament %>% filter(Position==1) %>% group_by(YEAR,PARTY) %>% summarise(CONSTITUENCIES_WON = n()) %>% filter(CONSTITUENCIES_WON==max(CONSTITUENCIES_WON))
kable(Year_result)
```

#### We can see from the output that the party INC has won the most number of elections in years 1951-2009


### Identify yearwise percentage of winning for female candidates?
```{r, message=FALSE, warning=FALSE}
Female_results = parliament %>% filter(Position==1) %>% group_by(YEAR) %>% summarise(PERCENT_FEMALE_WON = sum(Female)/n()*100)
kable(Female_results)
```

#### In this output we can see that highest number of female candidates to win the election was in the year 1992 



